\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2022-01-31 manuscript/paper.tex
Update the graphical representation

\subsection{Graphical model for the lights}
Figure~\ref{fig:graphical-model} below gives the graphical representation for the lights model to get a beter view of the dependence structure for the model.
\begin{figure}[!htb]
\centering
\resizebox{.9\textwidth}{!}{
\begin{tikzpicture}
\hspace{3cm}
\tikzstyle{main}=[circle, minimum size = 18mm, ultra thick, draw =black!80, node distance = 13mm,text centered]
\tikzstyle{var}=[rectangle, minimum size = 16mm, ultra thick, draw =black!80, node distance = 13mm,text centered]
\tikzstyle{connect}=[-latex, thick]
\tikzstyle{box}=[rectangle, draw=black!100]
  \node[var, fill = white!100] (beta) [] {\Large$\bm{\beta_k^l}$};
  \node[var, fill = white!100] (xi) [below=4cm of beta] {\Large$\bm{\xi_k}$};
  \node[var, fill = white!100] (gamma) [below=3cm of xi] {\Large$\bm{\gamma_k}$};
  \node[main, fill = white!100] (G) [right=4cm of xi] {\Large$\bm{G_i}$};
  \node[main, fill = white!100] (mu) [right=4cm of beta] {\Large$\bm{M_{ik}^l(t)}$};
  \node[main, fill = black!30] (Y) [right=of mu] {\Large$\bm{Y_i^l(t)}$};
  \node[main, fill = white!100] (b) [below=0.7cm of Y] {\Large$\bm{b_i^l}$};
  \node[var, fill = white!100] (phi) [above=of Y] {\Large$\bm{\phi_l}$};
  \node[var, fill = white!100] (Sigma) [right=of b] {\Large$\bm{D}$};
  \node[main, fill = white!100] (W) [below=of b] {\Large$\bm{\varphi_i(t)}$};
  \node[main, fill = white!100] (lambda) [right=4cm of gamma] {\Large$\bm{\lambda_i(t)}$};
  \node[main, fill = black!30] (T) [right=of lambda] {\Large$\bm{T_i}$};
  \node[main, fill = black!30] (X) at (3, -8.3) {\Large$\bm{X_i}$};

  \path [->,draw,ultra thick]
        (beta) edge (mu)
        (G) edge (mu)
        (b) edge (mu)
        (mu) edge (Y)
        (Sigma) edge (b)
        (phi) edge (Y)
        (xi) edge (G)
        (X) edge (G)
        (gamma) edge (lambda)
        (W) edge (lambda)
        (G) edge (lambda)
        (lambda) edge (T)
        ;

  \node[rectangle, inner sep=8mm,draw=black!100, ultra thick, fit= (beta) (xi) (gamma),label={[anchor=west, yshift=-0.5cm, xshift=-10mm]{\Large$\bm{k = 1...K}$}}] at (0, -4.6) {};
  \node[rectangle, inner sep=4mm,draw=black!100, ultra thick, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi)] {};
  \node[rectangle, inner sep=4mm, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi),ultra thick] at (12, 3.5) {\Large$\bm{l = 1...L}$};
  \node[rectangle, dashed, inner sep=3mm, draw=red!100, fit= (b) (W),ultra thick] {};

>>>>

\subsection{Graphical model for the lights}
Figure~\ref{fig:graphical-model} below gives the graphical representation for the lights model to get a beter view of the dependence structure for the model.
\begin{figure}[!htb]
\centering
\resizebox{.9\textwidth}{!}{
\begin{tikzpicture}
\hspace{3cm}
\tikzstyle{main}=[circle, minimum size = 18mm, ultra thick, draw =black!80, node distance = 13mm,text centered]
\tikzstyle{var}=[rectangle, minimum size = 16mm, ultra thick, draw =black!80, node distance = 13mm,text centered]
\tikzstyle{connect}=[-latex, thick]
\tikzstyle{box}=[rectangle, draw=black!100]
  \node[var, fill = white!100] (beta) [] {\Large$\bm{\beta_k^l}$};
  \node[var, fill = white!100] (xi) [below=4cm of beta] {\Large$\bm{\xi_k}$};
  \node[var, fill = white!100] (gamma) [below=3cm of xi] {\Large$\bm{\gamma_k}$};
  \node[main, fill = white!100] (G) [right=4cm of xi] {\Large$\bm{G_i}$};
  \node[main, fill = white!100] (mu) [right=4cm of beta] {\Large$\bm{M_{ik}^l(t)}$};
  \node[main, fill = black!30] (Y) [right=of mu] {\Large$\bm{Y_i^l(t)}$};
  \node[main, fill = white!100] (b) [above=of mu] {\Large$\bm{b_i^l}$};
  \node[var, fill = white!100] (phi) [above=of Y] {\Large$\bm{\phi_l}$};
  \node[var, fill = white!100] (Sigma) [left=of b] {\Large$\bm{D}$};
  \node[main, fill = black!30] (W) [below=3cm of Y] {\Large$\bm{\Psi_i}$};
  \node[main, fill = white!100] (lambda) [right=4cm of gamma] {\Large$\bm{\lambda_i(t)}$};
  \node[main, fill = black!30] (T) [right=of lambda] {\Large$\bm{T_i}$};
  \node[main, fill = black!30] (X) at (3, -8.3) {\Large$\bm{X_i}$};

  \path [->,draw,ultra thick]
        (beta) edge (mu)
        (G) edge (mu)
        (b) edge (mu)
        (mu) edge (Y)
        (Sigma) edge (b)
        (phi) edge (Y)
        (xi) edge (G)
        (X) edge (G)
        (gamma) edge (lambda)
        (W) edge (lambda)
        (G) edge (lambda)
        (lambda) edge (T)
        (Y) edge (W)
        ;

  \node[rectangle, inner sep=8mm,draw=black!100, ultra thick, fit= (beta) (xi) (gamma),label={[anchor=west, yshift=-0.5cm, xshift=-10mm]{\Large$\bm{k = 1...K}$}}] at (0, -4.6) {};
  \node[rectangle, inner sep=4mm,draw=black!100, ultra thick, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi)] {};
  \node[rectangle, inner sep=4mm, fit= (beta) (mu) (b) (Y) (b) (Sigma) (phi),ultra thick] at (8, 4.1) {\Large$\bm{l = 1...L}$};
